### 2014-11-12 tex/results.tex
adding a todo about the evaluation set up
Added label on results section

\section{Evaluation}

In this section we evaluate the effectiveness of \symtxt{} at
analyzing programs with unbounded complex data input in the context of
symbolic execution. In order to perform our evaluation we implement
the \symtxt{} technique and evaluate its efficiacy on three Java data
structure artifacts. We compare the results of \symtxt{} with other
state of the art techniques that initialize complex data input
symbolically. We first describe the tool infrastructure we use to
implement our approach.

@@

To perform our study we compile all our artifacts and run the analysis
on \nsr{the machine}.

>>>>

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of \symtxt{} at
analyzing programs with unbounded complex data input in the context of
symbolic execution. In order to perform our evaluation we implement
the \symtxt{} technique and evaluate its efficiacy on three Java data
structure artifacts. We compare the results of \symtxt{} with other
state of the art techniques that initialize complex data input
symbolically. We first describe the tool infrastructure we use to
implement our approach.

@@

To perform our study we compile all our artifacts and run the analysis
on \nsr{the machine.. sthuff about the time bound etc.}.
